---
title: "Untitled"
author: "Hongji Jiang"
date: "10/22/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Source my functions from last day

```{r}
source("http://tinyurl.com/rescale-R")
```

```{r}
rescale(1:10)
```

```{r}
rescale(c(1,10,5,NA,6))
```

```{r}
rescale2(c(1:10,"as"))

```

```{r}
rescale(c(1:10,"as"))
```

Write a function to find where there are NA elements in two input vectors
First make some simple input where I know the answer
```{r}
x<-c(1,2,NA,3,NA)
y<-c(NA,3,NA,3,4)
```

Looked online and found the **is.na()** function
```{r}
is.na(x)
```


and the **which()** function tells us where the TRUE values are 
```{r}
which(is.na(x))
```

```{r}
is.na(x)
is.na(y)
```

The AND function requires two input TRUE to give a true output
```{r}
is.na(x) & is.na(y)
```

Taking the **sum()** of TRUE FALSE vector will tell me how many TRUE elements I have 
```{r}
sum(is.na(x)&is.na(y))
```

```{r}
sum(TRUE,TRUE,FALSE)
```

Now turn it into function 

```{r}
both_na <- function(x,y){
  sum(is.na(x)&is.na(y))
}
```

```{r}
x <-  c(NA, NA, NA)
y1 <- c( 1, NA, NA)
y2 <- c( 1, NA, NA, NA,NA,NA)
both_na(x,y2)
```

```{r}
x2<-c(NA,NA)
both_na(x2,y2)
```

```{r}
plot(1:10,col=c('red','blue'))
```

```{r}
y3<-c(1,NA,NA,NA,NA,NA,NA)
length(x)
length(y3)
```


```{r}

both_na2 <- function(x,y){
  if(length(x) != length(y)){
    stop("Input x and input y should have the same length")
  }
  sum(is.na(x)&is.na(y))
}
```

```{r}
both_na2(x,y2)
```

```{r}
grade0 <- function(x){
  has_NA = FALSE
  for(i in x){
    if(is.na(i)){
      has_NA = TRUE
      x <- setdiff(x, i)
    }
  }
  if(has_NA){
    return(mean(x))
  }
  else
    return(mean(x[-which.min(x)]))
}
```

```{r}
# student 1
s1 <- c(100, 100, 100, 100, 100, 100, 100, 90) # student 2
s2 <-  c(100, NA, 90, 90, 90, 90, 97, 80)
```

```{r}
grade <- function(x){
  if(any(is.na(x))){
    warning("Student is missing a homework")
  }
  mean(x[which.min(x)],na.rm=TRUE)
}
```

```{r}
url <- "https://tinyurl.com/gradeinput"
hw <- read.csv(url, row.names = 1)
```

```{r}
apply(hw, 1, grade)
```

