---
title: "Class 8 machine learning"
author: "Hongji Jiang"
date: "10/24/2019"
output: github_document
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## K-means Clustering

```{r}
 # Generate some example data for clustering
tmp <- c(rnorm(30,-3), rnorm(30,3))
x <- cbind(x=tmp, y=rev(tmp))
plot(x)
```

Q. How many points are in each cluster?
Q. What ‘component’ of your result object details
      - cluster size?
      - cluster assignment/membership?
      - cluster center?
```{r}
k <- kmeans(x, centers=2, nstart=20)
k$size
k$cluster
k$centers
```

Plot x colored by the kmeans cluster assignment and
      add cluster centers as blue points
```{r}
plot(x, col = k$cluster)
points(k$centers,col = 12,pch = 15)
```

## Hierarchical clustering in R
The 'hclust()' function requires a distance matrix as input 
You can get this from 'dist()' function
```{r}
# First we need to calculate point (dis)similarity
#   as the Euclidean distance between observations
dist_matrix <- dist(x)
# The hclust() function returns a hierarchical
#  clustering model
hc <- hclust(d = dist_matrix)
# the print method is not so useful here
hc
```

```{r}
plot(hc)
abline(h=6,col='red')
cutree(hc,h=6)
```

```{r}
 # Step 1. Generate some example data for clustering
x <- rbind(
  matrix(rnorm(100, mean=0, sd = 0.3), ncol = 2),   # c1
  matrix(rnorm(100, mean = 1, sd = 0.3), ncol = 2), # c2
  matrix(c(rnorm(50, mean = 1, sd = 0.3),           # c3
           rnorm(50, mean = 0, sd = 0.3)), ncol = 2))
colnames(x) <- c("x", "y")
# Step 2. Plot the data without clustering
plot(x)
# Step 3. Generate colors for known clusters
#         (just so we can compare to hclust results)
col <- as.factor( rep(c("c1","c2","c3"), each=50) )
plot(x, col=col)
```

```{r}
kmeans(x,centers=3,nstart =20)
```

```{r}
#clustering
hc <- hclust(dist(x))

#draw tree
plot(hc)
abline(h=2,col='red')

#cut the tree into clusters/grps
grps <- cutree(hc,h=2)
grps
```

Plot the data colored by ther hcluster result with 
```{r}
plot(x,col = grps)
```

How many 
```{r}
table(grps)
```

Cross tablulate ie compare the clustering result with known answers
```{r}
table(grps,col)
```

```{r}
mydata <- read.csv("https://tinyurl.com/expression-CSV",
                        row.names=1)
head(mydata)


```
```{r}
dim(mydata)
```

#Principal component anylysis 
```{r}
## lets do PCA
pca <- prcomp(t(mydata), scale=TRUE)

attributes(pca)

plot(pca$x[,1],pca$x[,2])

pca.var <- pca$sdev^2
#1 is one significant figure
pca.var.per <- round(pca.var/sum(pca.var)*100,1)
pca.var.per
```

```{r}
barplot(pca.var.per, main="Scree Plot",
        xlab="Principal Component", ylab="Percent Variation")
```

```{r}
plot(pca$x[,1], pca$x[,2], 
     col= c('red','red','red','red','red','blue','blue','blue','blue','blue'))
```

```{r}
x <- read.csv("UK_foods.csv")

dim(x)

head(x)

rownames(x) <- x[,1]
x <- x[,-1]
head(x)

dim(x)
```

```{r}
barplot(as.matrix(x), beside=T, col=rainbow(nrow(x)))
```

```{r}
barplot(as.matrix(x),  col=rainbow(nrow(x)))
```

```{r}
pairs(x, col=rainbow(10), pch=1)
```

```{r}
pca <- prcomp(t(x))
summary(pca)
```

```{r}
plot(pca$x[,1],pca$x[,2])
pca$x
```

